### 2012-10-10 Docs/unit_tests/unit_tests.tex
renname docs Docs

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of 2-d the {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity
  field plus gradient of a scalar (x-component; center); and resulting
  velocity after projecting out the non-divergence free portion
  (x-component; right).  This is with slipwall boundary conditions on
  all sides, a 2-level grid with the left half refined and right half
  coarse, and the hgprojection tested.}
\end{figure}

>>>>

\begin{figure}[t] 
\centering
\includegraphics[height=1.9in]{\unitfigpath/wall_u_init_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_plus_grad_phi_x-velocity} 
\includegraphics[height=1.9in]{\unitfigpath/wall_u_new_x-velocity} 
%
\caption[Results of the 2-d {\tt test\_projection} unit test]{\label{fig:unit:projtest}
  Initial divergence free velocity field (x-component; left); Velocity
  field plus gradient of a scalar (x-component; center); and resulting
  velocity after projecting out the non-divergence free portion
  (x-component; right).  This is with slipwall boundary conditions on
  all sides, a 2-level grid with the left half refined and right half
  coarse, and the hgprojection tested.}
\end{figure}
